---
title: "Intro to R + Data Visualization - Suggested Answers"
---

For this ae, we'll use the **tidyverse** and **palmerpenguins** packages.

## Packages

```{r}
#| label: load-packages
#| warning: true 

library(tidyverse)
library(palmerpenguins) #The data set name is penguins
```

What are the `#|` above?

*code chunk arguments*

Which ones will we use during the semester? State and define them below.

message; turns of messages from output

warning; turns of warnings from output

eval; makes code chunk not run in the rendered output

echo; makes code not appear in rendered output

## Data

The dataset we will visualize is called `penguins`. Let's `glimpse()` at it.

```{r}
#| label: glimpse

glimpse(penguins)

```

Now, *pipe* the `penguins` data into the glimpse function to produce the same result.

```{r}
#| label: glimpse2

penguins |>
  glimpse()

```

What types of variables are we working with in this data set?

fct - factor - categorical int - integer - quantitative dbl - double - quantitative

**variables we don't see include: chr - character = words = categorical**

**log = logical = true/false = categorical**

# Visualizing penguin weights - Demo

## Useful links:

https://ggplot2.tidyverse.org/reference/

## Single variable

::: callout-note
Analyzing the a single variable is called **univariate** analysis.
:::

Create visualizations of the distribution of `weight`s of penguins.

1.  Make a histogram by filling in the `...` with the appropriate arguments. Set an appropriate binwidth. Hint: you can run `names(data.set)` in your console if you need a quick reminder on the variable names.

```{r}
#| label: histogram-weight


penguins |>
  ggplot( 
       aes(x = body_mass_g)) + #type variable name here
       geom_histogram() #type geom here

```

2.  Now, make a boxplot of `weight`s of penguins.

```{r}
#| label: boxplot-weight

penguins |>
  ggplot(
    aes(x = body_mass_g)
  ) + 
  geom_boxplot()

```

3.  Add a theme to your boxplot!

https://ggplot2.tidyverse.org/reference/ggtheme.html

```{r}
#| label: theme
#| eval: false

penguins |>
  ggplot(
    aes(x = body_mass_g)) + 
    geom_boxplot() + 
    theme_minimal() # type theme here

```

Why can / should we use themes?

**Looks nicer + can be more professional**

## Two variables

::: callout-note
Analyzing the relationship between two variables is called **bivariate** analysis.
:::

Create visualizations of the distribution of `weight`s of penguins by `species`. Note: `aes`thetic is a visual property of one of the objects in your plot. Aesthetic options are:

-   shape
-   color
-   size
-   fill

4.  Make a histogram of penguins' weight where the bars are colored in by species type. Set an appropriate binwidth and alpha value. At the same time, comment each line of code to articulate what it's doing.

```{r}
#| label: histogram-weight-species
#| eval: false

penguins |>
  ggplot( 
       aes(x = body_mass_g, size = species )) +
       geom_histogram(binwidth = 200, alpha = .5)

```

What happens when we change color to fill?

**When we make this change, it goes from outlining the objects to coloring them in.**
